### 2019-06-08 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Done, I changed := to \overset{.}{=}

\paragraph{Link with the MAB model.}
%
We consider the network from the point of view of one dynamic device.
Following a Bernoulli emission process, every time a dynamic device has to communicate with the gateway,
it has to choose one channel (at each transmission $t \geq 1, t \in \mathbb{N}$), denoted as $A(t) = k \in[K]$.
Then, the dynamic device waits in this channel $A(t)$ for an acknowledgement sent by the gateway, during a certain period (\eg, $5$ seconds for the example considered above).
Before sending another message (\ie, at time $t+1$), the dynamic device knows if it received or not this \Ack{} message.
%
For this reason, selecting channel (or arm) $k$ at time $t$ yields a (random) feedback, called a (binary) \emph{reward}, $r(t) := Y_{k,t} \in \{0,1\}$, being $0$ if no \Ack{} was received before the next message, or $1$ if \Ack{} was successfully received.
The goal of the dynamic device is to minimize its packet loss ratio, or equivalently, to maximize its number of successful transmissions, or its cumulative reward,
$\sum_{t = 1}^T r(t),$
which is the usual objective in MAB problems (see Section~\ref{sec:2:notations}).

@@

Where in the equation~\eqref{eq:41:Dilambda}, $(a)^{+} := \max(a,0)$, and $\mathcal{W}$ denotes the $\mathcal{W}$-Lambert function which is the reciprocal bijection of $x \mapsto x e^x$ on $\mathbb{R^+} = [0, +\infty)$ (which can be computed numerically in an efficient manner, \cite{Corless96}).
Moreover, condition \eqref{eq:41:eqCstr} implies that the Lagrange multiplier $\lambda$ is the solution of the constraint
\begin{equation}\label{eq:41:constraintLambda}
    \sum_{k=1}^{K} D_k^*(\lambda) = D.
\end{equation}

>>>>

\paragraph{Link with the MAB model.}
%
We consider the network from the point of view of one dynamic device.
Following a Bernoulli emission process, every time a dynamic device has to communicate with the gateway,
it has to choose one channel (at each transmission $t \geq 1, t \in \mathbb{N}$), denoted as $A(t) = k \in[K]$.
Then, the dynamic device waits in this channel $A(t)$ for an acknowledgement sent by the gateway, during a certain period (\eg, $5$ seconds for the example considered above).
Before sending another message (\ie, at time $t+1$), the dynamic device knows if it received or not this \Ack{} message.
%
For this reason, selecting channel (or arm) $k$ at time $t$ yields a (random) feedback, called a (binary) \emph{reward}, $r(t) \eqdef Y_{k,t} \in \{0,1\}$, being $0$ if no \Ack{} was received before the next message, or $1$ if \Ack{} was successfully received.
The goal of the dynamic device is to minimize its packet loss ratio, or equivalently, to maximize its number of successful transmissions, or its cumulative reward,
$\sum_{t = 1}^T r(t),$
which is the usual objective in MAB problems (see Section~\ref{sec:2:notations}).

@@

Where in the equation~\eqref{eq:41:Dilambda}, $(a)^{+} \eqdef \max(a,0)$, and $\mathcal{W}$ denotes the $\mathcal{W}$-Lambert function which is the reciprocal bijection of $x \mapsto x e^x$ on $\mathbb{R^+} = [0, +\infty)$ (which can be computed numerically in an efficient manner, \cite{Corless96}).
Moreover, condition \eqref{eq:41:eqCstr} implies that the Lagrange multiplier $\lambda$ is the solution of the constraint
\begin{equation}\label{eq:41:constraintLambda}
    \sum_{k=1}^{K} D_k^*(\lambda) = D.
\end{equation}
